Nested Sampling with Multiple Objective Functions

### 2018-06-03 doc/template.tex
Moving stuff into the newer template

%=================================================================
\documentclass[journal,article,submit,moreauthors,pdftex,10pt,a4paper]{Definitions/mdpi}

@@

%=================================================================
% Full title of the paper (Capitalized)
\Title{Title}

@@

% Authors, for the paper (add full first names)
\Author{Firstname Lastname $^{1,\dagger,\ddagger}$\orcidA{}, Firstname Lastname $^{1,\ddagger}$ and Firstname Lastname $^{2,}$*}

% Authors, for metadata in PDF
\AuthorNames{Firstname Lastname, Firstname Lastname and Firstname Lastname}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Affiliation 1; e-mail@e-mail.com\\
$^{2}$ \quad Affiliation 2; e-mail@e-mail.com}

% Contact information of the corresponding author
\corres{Correspondence: e-mail@e-mail.com; Tel.: +x-xxx-xxx-xxxx}

% Current address and/or shared authorship
\firstnote{Current address: Affiliation 3} 
\secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

@@

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{A single paragraph of about 200 words maximum. For research articles, abstracts should give a pertinent overview of the work. We strongly encourage authors to use the following style of structured abstracts, but without headings: 1) Background: Place the question addressed in a broad context and highlight the purpose of the study; 2) Methods: Describe briefly the main methods or treatments applied; 3) Results: Summarize the article's main findings; and 4) Conclusion: Indicate the main conclusions or interpretations. The abstract should be an objective representation of the article, it must not contain results which are not presented and substantiated in the main text and should not exaggerate the main conclusions.}

% Keywords
\keyword{keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific to the article, yet reasonably common within the subject discipline.)}

>>>>

%=================================================================
\documentclass[entropy,article,submit,moreauthors,pdftex,10pt,a4paper]{Definitions/mdpi}

@@

%=================================================================
% Full title of the paper (Capitalized)
\Title{Nested Sampling with Multiple Objective Functions}

@@

% Authors, for the paper (add full first names)
\Author{Brendon J. Brewer$^{1,}$*,
        Robert J. N. Baldock$^2$ and
        Ewan Cameron$^3$}

% Authors, for metadata in PDF
\AuthorNames{Brendon J. Brewer, Robert J. N. Baldock and Ewan Cameron}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Department of Statistics, The University of Auckland, Private Bag 92019,
Auckland 1142, New Zealand \\
$^{2}$ \quad TBD \\
$^{3}$ \quad TBD }

% Contact information of the corresponding author
\corres{Correspondence: bj.brewer@auckland.ac.nz}

% Current address and/or shared authorship
%\firstnote{Current address: Affiliation 3} 
%\secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

@@

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{We present a generalization of Skilling's Nested Sampling algorithm
that estimates
the partition function $Z(\beta_1, \beta_2)$ for a family of
probability distributions indexed by two hyperparameters, $\beta_1$ and
$\beta_2$. Problems like this arise frequently in statistical mechanics and
occasionally in Bayesian inference.
The algorithm is based on an interpretation of Nested Sampling in terms of
Sequential Monte Carlo, which produces unbiased estimates of $Z$ and therefore
allows parallel runs to be trivially combined.
We demonstrate the algorithm on three example problems:
(i)
a toy problem whose structure allows us
to accurately calculate $Z(\beta_1, \beta_2)$ numerically using non-Monte-Carlo
methods, so we can compute the actual error in the reconstructed function
$Z(\beta_1, \beta_2)$; (ii) a collection of atoms with a potential
that is intermediate between a Lennard-Jones form and a `polymer' form; and
(iii) A Bayesian image reconstruction example where the prior for the image
is defined conditionally on a hyperparameter, but where this prior contains
an intractable normalizing constant.
A free software implementation in C++ and Python is available at
\url{https://github.com/eggplantbren/TwinPeaks2018}.}

% Keywords
\keyword{nested sampling; bayesian computation; statistical mechanics;
         partition functions;
         sequential monte carlo; multi-objective optimization}
